
```{r}
library(Hmisc)
library(caret)
library(randomForest)
library(foreach)
library(doParallel)
options(warn=-1)
```


Setting the seed:

```{r}
set.seed(1234)
```

Let us load the data and get rid of errorneous data points:

```{r}    
trainData <- read.csv("~/Downloads/pml-training.csv", na.strings=c("#DIV/0!") )
evalData  <- read.csv("~/Downloads/pml-testing.csv", na.strings=c("#DIV/0!") )
```

Better transform columns to numeric:

```{r}    
    for(i in 8:(ncol(trainData)-1)) {
        trainData[,i] = as.numeric(as.character(trainData[,i]))
    }

for(i in 8:(ncol(evalData)-1)) {
    evalData[,i] = as.numeric(as.character(evalData[,i]))
}
```

What is the feature data:

```{r}    
featureData <- colnames(trainData[colSums(is.na(trainData)) == 0])[-(1:7)]
modelData   <- trainData[featureData]

myIndex  <- createDataPartition(y=modelData$classe, p=0.75, list=FALSE)
training <- modelData[myIndex,]
testing  <- modelData[-myIndex,]
```
Let us build random forests with 100 trees each. doParallel helps to do parallel computing instead of running simple loops:

```{r}
depend   <- training[-NCOL(training)]
independ <- training$classe

registerDoParallel()
myRandomForest <- foreach(noTrees=rep(100, 6), .combine=randomForest::combine, .packages='randomForest') %dopar% {
    randomForest(depend, independ, ntree=noTrees) 
}
```
Here is the error report:

```{r}
predictTraining <- predict(myRandomForest, newdata=training)
confusionMatrix(predictTraining,training$classe)

predictTesting <- predict(myRandomForest, newdata=testing)
confusionMatrix(predictTesting,testing$classe)
```

The test data has very high accuracy. It is quite satisfactory

Here we generate the submission files as provided by coursera:

```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

x <- evalData
x <- x[featureData[featureData!='classe']]
answers <- predict(myRandomForest, newdata=x)

pml_write_files(answers)
```
